The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-05-08 Moving temporal window - HESS/template.tex
HESS minor corrections.

	The second approach was used to obtain data that are closer to the chronology of the actual precipitation by relying on informative proxy variables during the reconstruction procedure. Data from NCEP/NCAR reanalysis 1 were used for this purpose. Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment. Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition. Time lapses from -12 h to +12 h between both series were introduced to consider the significant distance separating the weather stations and the reanalysis grid point. The best proxy variable, precipitable water, was identified through correlation analyses on non-zero values with the 6-h precipitation time series. When the best proxy was selected, its temporal profile was used to disaggregate the daily precipitation time series.

	These two simple methods did not result in valuable outputs (results not shown). Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the reconstructed precipitation archives. A slight improvement was obtained for the second method which relied on a proxy variable rather than the proportional distribution method. However, this  improvement was relatively small, and most of the benefit of the MTW was lost. Another reanalysis dataset with more accurate moisture variables could produce better proxies.

@@

	The importance of the quality of the precipitation archive was also demonstrated because simplistic reconstructions of sub-daily time series led to a loss of all the improvement brought by the MTW. The precipitation prediction improved only when the precipitation chronology was close to the accurate values. Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP/NCAR reanalysis 1 dataset as a proxy were not successful. Other reanalysis datasets with more accurate moisture variables could show better performance.

	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy. The precipitation data archives of high temporal resolution have increased over time. Other possible sources of such archives is the establishment of precipitation reanalysis at a regional scale in addition to the use of reanalysis-driven regional climate models or limited area models over a long period. Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.

	The introduction of the MTW improved the selection of synoptic analogues. Regardless of its impact on the prediction skill for precipitation or the availability of a predictand time series with a sub-daily time step, this improvement has the potential for application to long meteorological archives. For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, it can be used even if no precipitation archive is available. Thus, it is worth knowing whether the situation at hand had such an analogue in the past. Another possible application is quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data are available. Indeed, if the selection of analogues with the MTW on a long period for a specific target day differs from the selection for the shorter period, a sub-optimal forecast could be identified. Finally, some other predictands might not need sub-daily total values but point observations such as hail or extreme wind gusts, which make them easier to use with the MTW.

>>>>

	The second approach was used to obtain data that are closer to the chronology of the actual precipitation by relying on informative proxy variables during the reconstruction procedure. Data from NCEP/NCAR reanalysis 1 were used for this purpose. Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment and at different times of the day. Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition. The best proxy variable, precipitable water, was identified through correlation analyses with the 6-h precipitation time series on the period 1982--2007 (on non-zero precipitation values). When the best proxy was selected, its temporal profile was used to disaggregate the daily precipitation time series.

	These two simple methods did not result in valuable outputs (results not shown). Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the reconstructed precipitation archives. The second method which relied on a proxy variable performed slightly better than the proportional distribution method, but not enough to obtain a relevant time series. Another reanalysis dataset with more accurate moisture variables could produce better proxies.

@@

	It is desirable for the AM to have available the biggest pool of candidate analogues. By inflating the archive, the MTW contributes to enriching this pool. However, the use of the MTW relies partly on precipitation series at a sub-daily time step, which are available for the last decades. It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the recent period. Attempts to reconstruct longer sub-daily precipitation time series based on simple disaggregation methods were not successful, which demonstrated the importance of the quality of the precipitation archive to be used in the MTW technique. The precipitation prediction provided by the MTW improved only when the precipitation chronology was close to the accurate values. More advanced disaggregation methods might provide suitable sub-daily time series. Alternatively, another option could be to combine both the MTW and the classical approach and to look for analogue situations at a sub-daily time step from the 80's and at a daily time step for the antecedent years. Finally, some other predictands might not need sub-daily total values but point observations such as the occurrence of hail or extreme wind gusts, which make them easier to use with the MTW as no disaggregation is needed.

	The introduction of the MTW improved the selection of synoptic analogues. Regardless of the availability of precipitation series at a sub-daily time step, the MTW can be used to provide a better diagnostic of the weather situation of the target date. It can be used for example to identify analogue dates related to extreme weather conditions in historical databases.
